### 2010-03-25 thesis/SensorMLOnSenseTile/trunk/thesis/SensorMLonSenseTileThesis.tex
latest

SenseTile is a sensor and processing package that can contain motion sensors, RFID sensors, temperature sensor, audio sensors, pressure sensors, light level sensors video sensors among others. It is used as a replacement for standard ceiling tiles to provide smart building services as part of a Web Sensor Network. The SenseTile System is made up of two units a Sensor Board and Processor Unit. The sensors are interfaced or hosted on the Sensor Board. The Processor Unit interfaces to the Sensor Board allowing data from the Sensor Board to be processed futher as required.

@@

There are othe  SOS specification depend on another SWE specification, Observation and Measurements(O\&M)[ref]. This specification provides standard models and XML encoding for sensor observations.

@@

\section{BON to SensorML mapping}
Features to be elements or attributes.

Name rule suffix "Attrib" to make it an attribute.

List handling - convention for mapping.

SML prefix to handled key word clashes between sensorML and BON.

@@

\begin{figure}[h]
\framebox{\scalebox{0.65}{\includegraphics{GetObs.png}}}
\caption{Get Observation from Sensor}\label{fig:GetObs}
\end{figure}
\newpage
\subsection{SenseTile WebService Network Architecture}
\label{subsec:SenseTile WebService Network Architecture}
In the SenseTile Web Service the SOS acts as a gateway to the SenseTile Sensor Network. This prototype was designed with the network architecture as shown in fig \ref{fig:Deployment_network}. A client accesses multiple SOS instances to get observations from the sensor network. An SOS can support several DataProducers and hence would not to be run on every SenseTile Unit.

\begin{figure}[h]
\scalebox{0.65}{\includegraphics{Deployment_sensetile_network.png}}
\caption{SenseTile Sensor Network Architecture}\label{fig:Deployment_network}
\end{figure}
The SOS Specification envisioned that the SOS is run on a large external server as shown in fig \ref{fig:Deployment_ext_sos}. The DataProducers update this external server with observations and SOS Data Consumer access this large SOS.
\begin{figure}[h]
\scalebox{0.65}{\includegraphics{Deployment_sensetile_ext_sos.png}}
\caption{External SOS}\label{fig:Deployment_ext_sos}
\end{figure}
The SOS Specification describes the use of a Proxy SOS as shown in figure \ref{fig:Deployment_sos_aggr}. This architecture could be used with the SenseTile Sensor Network if accessing many SOSs is not feasible for the clients.
\begin{figure}[h]
\scalebox{0.65}{\includegraphics{Deployment_sensetile_sos_aggr.png}}
\caption{Proxy SOS}\label{fig:Deployment_sos_aggr}
\end{figure}

@@

Questions.
If have light data but no temp. As temp is only
every 1000 packets?

How to know when to generate observation
for the two offerings?
DataProducer generates observations in Observation xml standard.

Interface to the SensorBoard Library.

Uses observer pattern to update sensors with packets from the board.

reads sensors from SensorBoard System xml

Sensors implement interface to facilitate this.

Vast lib connects all the processes

implementation of sensor and convertor is named using URN read from the sensorMl descption.

@@

Interfaces to the Sensor Board

@@

\chapter{ Conclusions and Future Work}
There seems to be work ongoing to change this to a more industry standard view of Web Services with the use of WSDL/SOAP. I could not find this as part of current OGC SWE framework.
what has been achieved

the weaknesses of your approach
SOS on the Processor Board. Is this right.

difficult schemas to program against.
JIBX did not generate a default binding.
Jaxb did with some help but did not generate the process type correctly.
Why?

Difficult to get connections correct. Excute the model to find problems.
Need static checking.
Definitely need a tool to generate SensorML. BON would
help even if metadata not covered. Could be add by
style sheet.

Schemas cover all needs for sensor description and data.

A lot of schemas needed.

SWE not fully web services as W3C might define. Not SOAP. HTTP envelope
flexible.

Vast Lib use as a references only. Other ways such a XQUERY? XML techs?
As there are a large number of types etc. A quick way for a prototype.
Had to update library code to get it to work with the SenseTile Schemas. Schemas
passed the validation test tool from the site.

Portabiltiy, Vast Types POJOs.

pointed to implenentation would need to be developed for a specific
SensorML engine.

further work.
Complete BON and parser.
Streaming the data. See Arch doc.

>>>>

SenseTile is a sensor and processing package that can contain motion sensors, RFID sensors, temperature sensor, audio sensors, pressure sensors, light level sensors video sensors among others. It is used as a replacement for standard ceiling tiles to provide smart building services as part of a Web Sensor Network. The SenseTile System is made up of two units a Sensor Board and Processor Unit. The sensors are interfaced or hosted on the Sensor Board. The Processor Unit interfaces to the Sensor Board allowing data from the Sensor Board to be processed further as required.

@@

There are other SOS specification depend on another SWE specification, Observation and Measurements(O\&M)[ref]. This specification provides standard models and XML encoding for sensor observations.

@@

\section{BON to SensorML mapping}

@@

\begin{figure}[h]
\framebox{\scalebox{0.65}{\includegraphics{GetObs.png}}}
\caption{Get Observation from Sensor}\label{fig:GetObs}
\end{figure}
\newpage
\subsection{SenseTile WebService Network Architecture}
\label{subsec:SenseTile WebService Network Architecture}
In the SenseTile Web Service the SOS acts as a gateway to the SenseTile Sensor Network. This prototype is designed with the network architecture as shown in fig \ref{fig:Deployment_network}. A client accesses multiple SOS instances to get observations from the sensor network. An SOS can support several DataProducers and hence would not to be run on every SenseTile Unit.

\begin{figure}[h]
\scalebox{0.65}{\includegraphics{Deployment_sensetile_network.png}}
\caption{SenseTile Sensor Network Architecture}\label{fig:Deployment_network}
\end{figure}
The SOS Specification envisioned that the SOS is run on a large external server as shown in fig \ref{fig:Deployment_ext_sos}. The DataProducers update this external server with observations and SOS Data Consumer access this large SOS.
\begin{figure}[h]
\scalebox{0.65}{\includegraphics{Deployment_sensetile_ext_sos.png}}
\caption{External SOS}\label{fig:Deployment_ext_sos}
\end{figure}

The SOS Specification describes the use of a Proxy SOS as shown in figure \ref{fig:Deployment_sos_aggr}. This architecture could be used with the SenseTile Sensor Network if accessing many SOSs is not feasible for the clients.
\begin{figure}[h]
\scalebox{0.65}{\includegraphics{Deployment_sensetile_sos_aggr.png}}
\caption{Proxy SOS}\label{fig:Deployment_sos_aggr}
\end{figure}

@@

@@

@@

\chapter{ Conclusions and Future Work}
This thesis analyses the role SensorML plays in Sensor Web Networks. The UCD CASL SenseTile System is used a case study with the development of the SenseTile Web Service to access the SenseTile System sensor data. SensorML alone is not sufficient to model all aspects of Sensor Web Networks but is focused on providing a standard way to exchange sensor metadata, describing sensor input/output data and the processing of sensor data. This leads to examining other OGC SWE specifications, of which SensorML is one. The SWE SOS specification describes the operations for accessing sensor observations and it's concepts were used to develop the SenseTile Web Service. It uses SensorML provide sensor metadata to clients and the O\&M specification to encode observations. The OGC SWE initiative is trying to standardize a Web Service approach to accessing and processing sensor data.

SensorML is relatively intuitive but it is difficult to know if one has developed a "good" SensorML model. There are examples and tutorials to help.

The SenseTile model uses a hierarachy to model the SenseTile. It seems repetitive to have keep defining the same inputs for each contained component. Maybe this is a flaw in the SenseTile model developed.

Working in XML is error prone. SensorML connections type was a good example of where a graphical tool or another language, like BON,  that can be parsed should be used to check the connections. Running the model through the VastSensorMLEngine without a crash was only way other than by eye to see that the connections were set up correctly.

SensorML is defined by a heavy XML Schema. This XML Schema along with the other XML Schema for the SOS and dependent specifications are heavy indeed. Achieving a Java binding was difficult. JIBX would not generate a default XML binding. JAXB could with some help. There are many layers of abstraction in these XML Schema. This reflects the that the specifications cover a very wide range of needs of a senor system.

The idea of automatically obtaining a SensoML model and executing it depends on the SensorML Engine being used. Only one Java implementation can be pointed. In the OGC examples the Java implementations of the

Vast Lib use as a references only.
Had to update library code to get it to work with the SenseTile schema even though the schema
passed the validation test tool from the site. It uses DOM but XML binding is probably a better approach.

the weaknesses of your approach
-----------------------------------------
SOS on the Processor Board. Is this right? RMI only useful if SenseTile Network is a lan.

SWE not fully web services as W3C might define. Not SOAP. HTTP envelope
flexible. There seems to be work ongoing to change this to a more industry standard view of Web Services with the use of WSDL/SOAP. I could not find this as part of current OGC SWE framework.
what has been achieved

further work.
---------------
Complete BON mapping and parser.
Streaming the data. See SWE Architecture dpcument for a description of one approach.
Other technology approaches such as . Other ways such a XQUERY? XML techs?
